Using numerical modelling to investigate temperature and wave exposure as drivers

### 2019-12-01 morphology_paper.Rmd
changes to yaml, added scritp to save plot panels, and then some

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers
  of macroalgal morphological characteristics
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
output:
  word_document:
    reference_docx: frontiers_template.docx
  pdf_document:
    fig_caption: yes
  html_document:
    df_print: paged
bibliography: references.bib
papersize: A4
tables: yes
abstract: 'Macroalgal morphological variation is determined to a large extent by
  a combination of environmental factors, with wave exposure and temperature
  perhaps the main influences as they are key environmental properties to which a species becomes locally adapted.                Macroalgae have shown to exhibit different responses to different magnitudes of exposure to waves, such as reduction
  in overall size and strength increasing traits. In terms of temperature, warmer
  environments have been shown to reduce the overall size of resident and transplanted
  species. However, none of the past studies have identified specific wave and temperature
  metrics responsible for the morphological adaptation macroalgae exhibit. Past research
  has often used simple or two-dimensional models of wave exposure, which do not
  take into account important aspects of the nearshore environment such as wave breaking,
  refraction and diffraction. Furthermore, past studies have often used satellite-derived
  datasets as sources for temperature data; however, such data have been shown to have large bias when 
  applied to the nearshore environment. This study used *in situ* temperature data and wave power
  metrics calculated from a 3D-numerical model to identify specific temperature and wave metrics
  responsible for morphological adaptation of the kelp, *Ecklonia maxima* and *Laminaria pallida*. The results identify wave      exposure as the main driver of morphological adaptation while identifying specific wave metrics.
  Furthermore, the results show differences in wave metrics between species; and between
  deep and shallow populations.'
---

@@

wave_boxplot_1 <- ggplot(data = wave_ann_meta, aes(x = region, y = hs_mean, fill  = region)) + 
  geom_boxplot(show.legend = FALSE) + 
  stat_compare_means(label.y =0.6 ,label.x = 2.5, label = "p.signif") + 
  xlab("") + 
  ylab("") + 
  coord_flip() + 
  theme_bw() +
  scale_fill_grey(start = 0.4, end = 0.8) + 
  theme(axis.text.y=element_text(vjust=0.3))

wave_boxplot_2 <- ggplot(data = wave_ann_meta, aes(x = region, y = tp_mean, fill  = region)) + 
  geom_boxplot(show.legend = FALSE) + 
  stat_compare_means(label.y = 8.2, label.x = 2.5, label = "p.signif") + 
  xlab("") + 
  ylab("") +
  ylim(8,12) + 
  coord_flip() + 
  theme_bw() +
  scale_fill_grey(start = 0.4, end = 0.8) + 
  theme(axis.text.y=element_text(vjust=0.3))

@@

@@

@@

@@

@@

LT6 <- ggplot(data = lam_data, aes(x = temp_regime, y = stipeDiameter, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp)  + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.65, label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Stipe diameter (cm)") +
  scale_fill_discrete(name="Temperature regime") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

LW8 <- ggplot(data = lam_data, aes(x = wave_exposure, y = thallusMass, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure_lam) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE) +
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.x  = 0.9, label.y.npc = c('top')) + 
  ylab("Thallus mass (kg)") + 
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level")) +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("")
LW9 <- ggplot(data = lam_data, aes(x = wave_exposure, y = totalLength, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure_lam) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE) +
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.x  = 0.9, label.y.npc = c('top')) + 
  ylab("Total length (cm)") + 
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level")) +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("")
```

@@

pos_temp <- c("Cool temperate", "Warm temperate") #custom temperature categories position on x-axis
#temperature plots made seperately for each morphological characteristic
ET1 <- ggplot(data = eck_deep, aes(x = temp_regime, y = frond_mass, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET2 <- ggplot(data = eck_deep, aes(x = temp_regime, y = primary_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Primary length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET3 <- ggplot(data = eck_deep, aes(x = temp_regime, y = primary_width, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Primary width (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET4 <- ggplot(data = eck_deep, aes(x = temp_regime, y = frond_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET5 <- ggplot(data = eck_deep, aes(x = temp_regime, y = stipe_mass, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET6 <- ggplot(data = eck_deep, aes(x = temp_regime, y = stipe_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET7 <- ggplot(data = eck_deep, aes(x = temp_regime, y = stipe_circ, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET8 <- ggplot(data = eck_deep, aes(x = temp_regime, y = tufts, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET9 <- ggplot(data = eck_deep, aes(x = temp_regime, y = epi_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Epi length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)
ET10 <- ggplot(data = eck_deep, aes(x = temp_regime, y = total_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = TRUE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

@@

# custom positions for wave exposure categories and sites
pos_exposure <- c("Fully sheltered", "Extremely sheltered", "Very sheltered","Moderately exposed", "Exposed", "Very exposed")
#morphology and wave exposure
EW1 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = frond_mass, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  guides(fill=guide_legend(title="Wave exposure level")) 
EW2 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = primary_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  ylab("Primary length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  guides(fill=guide_legend(title="Wave exposure level"))  
EW3 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = primary_width, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Primary width (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  guides(fill=guide_legend(title="Wave exposure level"))  
EW4 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = frond_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  guides(fill=guide_legend(title="Wave exposure level"))  
EW5 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_mass, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  guides(fill=guide_legend(title="Wave exposure level"))  
EW6 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  guides(fill=guide_legend(title="Wave exposure level"))  
EW7 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_circ, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Stipe circumference (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  guides(fill=guide_legend(title="Wave exposure level"))  
EW8 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = tufts, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("No of Tufts") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  guides(fill=guide_legend(title="Wave exposure level"))  
EW9 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = epi_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Epi length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +

>>>>

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers
  of macroalgal morphological characteristics
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
output:
  word_document:
    reference_docx: frontiers_template.docx
  pdf_document:
    fig_caption: yes
  html_document:
    df_print: paged
bibliography: references.bib
papersize: A4
tables: yes
abstract:  '**Abstract**: Macroalgal morphological variation is determined to a large extent by
  a combination of environmental factors, with wave exposure and temperature
  perhaps the main influences as they are key environmental properties to which a species becomes locally adapted.                Macroalgae have shown to exhibit different responses to different magnitudes of exposure to waves, such as reduction
  in overall size and strength increasing traits. In terms of temperature, warmer
  environments have been shown to reduce the overall size of resident and transplanted
  species. However, none of the past studies have identified specific wave and temperature
  metrics responsible for the morphological adaptation macroalgae exhibit. Past research
  has often used simple or two-dimensional models of wave exposure, which do not
  take into account important aspects of the nearshore environment such as wave breaking,
  refraction and diffraction. Furthermore, past studies have often used satellite-derived
  datasets as sources for temperature data; however, such data have been shown to have large bias when 
  applied to the nearshore environment. This study used *in situ* temperature data and wave power
  metrics calculated from a 3D-numerical model to identify specific temperature and wave metrics
  responsible for morphological adaptation of the kelp, *Ecklonia maxima* and *Laminaria pallida*. The results identify wave      exposure as the main driver of morphological adaptation while identifying specific wave metrics.
  Furthermore, the results show differences in wave metrics between species; and between
  deep and shallow populations.'

nocite:  |
  @Algaebase
---

@@

wave_boxplot_1 <- ggplot(data = wave_ann_meta, aes(x = region, y = hs_mean, fill  = region)) + 
  geom_boxplot(show.legend = FALSE) + 
  stat_compare_means(label.y =0.6 ,label.x = 2.5, label = "p.signif") + 
  xlab("") + 
  ylab("") + 
  coord_flip() + 
  theme_bw() +
  scale_fill_grey(start = 0.4, end = 0.8) + 
  theme(axis.text.y=element_text(vjust=0.3)) 
ggsave("hs_plot.jpeg", plot = wave_boxplot_1, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

wave_boxplot_2 <- ggplot(data = wave_ann_meta, aes(x = region, y = tp_mean, fill  = region)) + 
  geom_boxplot(show.legend = FALSE) + 
  stat_compare_means(label.y = 8.2, label.x = 2.5, label = "p.signif") + 
  xlab("") + 
  ylab("") +
  ylim(8,12) + 
  coord_flip() + 
  theme_bw() +
  scale_fill_grey(start = 0.4, end = 0.8) + 
  theme(axis.text.y=element_text(vjust=0.3))
ggsave("tp_plot.jpeg", plot = wave_boxplot_2, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig8A.jpeg", plot = LT1, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig8B.jpeg", plot = LT2, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig8C.jpeg", plot = LT3, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig8D.jpeg", plot = LT4, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig8E.jpeg", plot = LT5, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

LT6 <- ggplot(data = lam_data, aes(x = temp_regime, y = stipeDiameter, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp)  + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.65, label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Stipe diameter (cm)") +
  scale_fill_discrete(name="Temperature regime") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey()

ggsave("fig8F.jpeg", plot = LT6, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig8G.jpeg", plot = LT7, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig8H.jpeg", plot = LT8, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig8I.jpeg", plot = LT9, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig9A.jpeg", plot = LW1, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig9B.jpeg", plot = LW2, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig9C.jpeg", plot = LW3, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig9D.jpeg", plot = LW4, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig9E.jpeg", plot = LW5, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig9F.jpeg", plot = LW6, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

ggsave("fig9G.jpeg", plot = LW7, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

LW8 <- ggplot(data = lam_data, aes(x = wave_exposure, y = thallusMass, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure_lam) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE) +
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.x  = 0.9, label.y.npc = c('top')) + 
  ylab("Thallus mass (kg)") + 
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level")) +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("")

ggsave("fig9H.jpeg", plot = LW8, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

LW9 <- ggplot(data = lam_data, aes(x = wave_exposure, y = totalLength, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure_lam) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE) +
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.x  = 0.9, label.y.npc = c('top')) + 
  ylab("Total length (cm)") + 
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level")) +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("")

ggsave("fig9I.jpeg", plot = LW9, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

pos_temp <- c("Cool temperate", "Warm temperate") #custom temperature categories position on x-axis
#temperature plots made seperately for each morphological characteristic
ET1 <- ggplot(data = eck_deep, aes(x = temp_regime, y = frond_mass, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Frond mass (g)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10A.jpeg", plot = ET1, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET2 <- ggplot(data = eck_deep, aes(x = temp_regime, y = primary_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Primary length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10B.jpeg", plot = ET2, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET3 <- ggplot(data = eck_deep, aes(x = temp_regime, y = primary_width, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Primary width (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10C.jpeg", plot = ET3, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET4 <- ggplot(data = eck_deep, aes(x = temp_regime, y = frond_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Frond length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10D.jpeg", plot = ET4, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET5 <- ggplot(data = eck_deep, aes(x = temp_regime, y = stipe_mass, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Stipe mass (g)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10E.jpeg", plot = ET5, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET6 <- ggplot(data = eck_deep, aes(x = temp_regime, y = stipe_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Stipe length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10F.jpeg", plot = ET6, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET7 <- ggplot(data = eck_deep, aes(x = temp_regime, y = stipe_circ, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Stipe circ (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10G.jpeg", plot = ET7, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET8 <- ggplot(data = eck_deep, aes(x = temp_regime, y = tufts, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("No. of tufts") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10H.jpeg", plot = ET8, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET9 <- ggplot(data = eck_deep, aes(x = temp_regime, y = epi_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = FALSE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Epi length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10I.jpeg", plot = ET9, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

ET10 <- ggplot(data = eck_deep, aes(x = temp_regime, y = total_length, fill = temp_regime)) +
  scale_x_discrete(limits = pos_temp) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = FALSE, show.legend = TRUE) + 
  stat_compare_means(method = "wilcox.test", label = "p.signif", label.x  = 0.6, label.y.npc = c('top')) + 
  ylab("Total length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_grey(start = 0.8, end = 0.4)

ggsave("fig10J.jpeg", plot = ET10, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

@@

# custom positions for wave exposure categories and sites
pos_exposure <- c("Fully sheltered", "Extremely sheltered", "Very sheltered","Moderately exposed", "Exposed", "Very exposed")
#morphology and wave exposure
EW1 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = frond_mass, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Frond mass (g)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level"))

ggsave("fig11A.jpeg", plot = EW1, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

EW2 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = primary_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  ylab("Primary length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level"))

ggsave("fig11B.jpeg", plot = EW2, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

EW3 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = primary_width, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Primary width (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level"))

ggsave("fig11C.jpeg", plot = EW3, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

EW4 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = frond_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Frond length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level"))

ggsave("fig11D.jpeg", plot = EW4, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

EW5 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_mass, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Stipe mass (g)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level"))

ggsave("fig11E.jpeg", plot = EW5, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")

EW6 <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA, varwidth = TRUE, notch = TRUE)  + 
  stat_compare_means(method = "kruskal.test", label = "p.signif", label.y.npc = c('top')) + 
  xlab("") + 
  ylab("Stipe length (cm)") +
  theme_bw() +
  theme(axis.text.x = element_blank()) + 
  xlab("") +
  scale_fill_brewer(palette="OrRd") +
  guides(fill=guide_legend(title="Wave exposure level"))

ggsave("fig11F.jpeg", plot = EW6, dpi = 300, device = "jpeg", path = "extra/morphology_paper_prep/")
